\newcommand{\MzFam}{\textit{MzFAM}}

\documentclass[twoside]{report}

\title{MzFAM: A File Alteration Monitor for MzScheme}
\author{Jos\'e Antonio Ortega Ruiz <jao@gnu.org>}
\date{}

\chapter{Introduction}
\label{cha:introduction}

\MzFam\ provides a series of Scheme utilities to monitor and react to
filesystem changes. It exports a high-level interface consisting of
monitoring tasks that run as independent threads and invoke callback
procedures each time a file alteration is detected. These high-level
tasks (provided by the module \scm{fam-task}) are implemented using
either Linux's FAM/Gamin monitor or, in systems (like Windows) where
it is not available, a pure Scheme fall-back implementation. This
low-level functionality is in turn provided by two modules (\scm{fam}
and \scm{fam-mz}, respectively) which share the generic interface
defined by the \scm{fam-base} module. You may use \scm{fam} or
\scm{fam-mz} directly (bypassing the high-level interface) if you find
\scm{fam-task} not suitable for your needs. The generic functions in
\scm{fam-base} are, basically, one-to-one counterparts of those
provided by the \texttt{libfam} C library.

Chapter~\ref{cha:fam-tasks} describes FAM tasks, and should provided
all the information needed to use \MzFam\ in your programs. In case
you need more fine-grained control over your file-monitoring, turn to
chapter~\ref{cha:low-level-interface}, which describes the generic
interface exported by the \scm{fam-base} module and implemented by
\scm{fam} (using \texttt{libfam} (or \texttt{libgamin})) and by
\scm{fam-mz} (using Scheme).

\include{fam-task}
\include{fam}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
